Workflow of Inverse Model for Rooting Profiles

### 2020-04-05 Workflow.Rmd
Code rearrangement after rooting profiles changed; and together wit the last commit edits towards running a sensitivity analyses by removing several dry season months in Btran calculations for deciduous species

```{r Chunk 1.0, eval = FALSE}
source("code/1.GLUEsetup_part1_BCI.R")
GLUEsetup_part1(current.folder = "2019-10-14_5000", intervals = 5) # this can take 30 min to get btran by nsam
```

```{r Chunk 2, eval = FALSE}
source("code/4.1.GLUEsetup_part2_BCI.R")
GLUEsetup_part2(growth.type = "med", dbh.residuals = "off", solar.residuals = "off", 
                growth.selection = "size_class_predefined_cc_scaled") #"size_class_varying_non_cc") #n.ensembles = 100000
# growth.type = "med"; dbh.residuals = "off"; solar.residuals = "off"; growth.selection = "size_class_predefined_cc_scaled"
```

```{r Chunk 3, eval = TRUE}
# This sources "code/4.2GLUErun_part2_func_BCI.R"
source("code/4.3.GLUErun_part2_BCI.R")
GLUE_run(splevel = "off", goodness.fit = 0.3)
# GLUE_run(splevel = "on", goodness.fit = 0.3)
```

@@

```{r Chunk 4, eval = TRUE}
source("code/4.5.prep.udi.calculator.R")
prep.udi.calculator(splevel = "on")
prep.udi.calculator(splevel = "off")
```

```{r Chunk 5, eval = TRUE}
source("code/4.6.udi.calculator.R")
##---needs to be run manually on macbook for splevel = "off" and iso.subset = "off"---
# udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.5, iso.subset = "on") ## udi is not calculated below this rsq.thresh
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; iso.subset = "on"
# udi.calculator(splevel = "on", dryseason = "off", rsq.thresh = 0.5, iso.subset = "on") 
# udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.5, iso.subset = "on")
udi.calculator(splevel = "off", dryseason = "jan", rsq.thresh = 0.5, iso.subset = "on")
udi.calculator(splevel = "on", dryseason = "jan", rsq.thresh = 0.5, iso.subset = "on")
# udi.calculator(splevel = "off", dryseason = "1992", rsq.thresh = 0.5, iso.subset = "off") 
# udi.calculator(splevel = "on", dryseason = "1992", rsq.thresh = 0.5, iso.subset = "off")
```

```{r Chunk 6, eval = TRUE}
source("code/4.7.summarising_udi_by_sp_size.R")
# summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; root.selection = "on"; iso.subset = "off"
# summarise.udi(splevel = "on", dryseason = "off", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# summarise.udi(splevel = "off", dryseason = "off", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
summarise.udi(splevel = "on", dryseason = "jan", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
summarise.udi(splevel = "off", dryseason = "jan", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
```

```{r Chunk 7, eval = TRUE}
source("code/10.Comparison_with_Meinzer1999.R")
```

>>>>

```{r Chunk 1.0, eval = FALSE}
source("code/4.1.1.GLUEsetup_part1_BCI.R")
GLUEsetup_part1(current.folder = "2019-10-14_5000", intervals = 5) # this can take 30 min to get btran by nsam
```

```{r Chunk 2, eval = FALSE}
source("code/4.1.2.GLUEsetup_part2_BCI.R")
GLUEsetup_part2(growth.type = "med", dbh.residuals = "on", solar.residuals = "off", 
                growth.selection = "size_class_predefined_cc_scaled") #"size_class_varying_non_cc") #n.ensembles = 100000
# growth.type = "med"; dbh.residuals = "on"; solar.residuals = "off"; growth.selection = "size_class_predefined_cc_scaled"
```

```{r Chunk 3, eval = TRUE}
# This sources "code/4.2GLUErun_part2_func_BCI.R"
source("code/4.3.GLUErun_part2_BCI.R")
# splevel = "on"; goodness.fit = 0.3; drop.months = "Mar"
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "off", goodness.fit = 0.3, drop.months = "FebMar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Feb")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "Mar")
GLUE_run(splevel = "on", goodness.fit = 0.3, drop.months = "FebMar")
```

@@

```{r Chunk 4, eval = TRUE}
source("code/4.5.prep.udi.calculator.R")
# splevel = "on"; drop.months = "JanFebMar"
prep.udi.calculator(splevel = "on", drop.months = "Feb")
prep.udi.calculator(splevel = "on", drop.months = "FebMar")
prep.udi.calculator(splevel = "on", drop.months = "Mar")

prep.udi.calculator(splevel = "off", drop.months = "Feb")
prep.udi.calculator(splevel = "off", drop.months = "FebMar")
prep.udi.calculator(splevel = "off", drop.months = "Mar")
```

```{r Chunk 5, eval = TRUE}
source("code/4.6.udi.calculator.R")
##---needs to be run manually on macbook for splevel = "off" and iso.subset = "off"---
# udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.5, iso.subset = "on") ## udi is not calculated below this rsq.thresh
# splevel = "on"; dryseason = "on"; rsq.thresh = 0.5;  n.ci.thresh = 3; iso.subset = "on"; drop.months = "JanFebMar"
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "Feb")
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "FebMar")
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "Mar")

udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "Feb")
udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "FebMar")
udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "on", drop.months = "Mar")

udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "Feb")
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "FebMar")
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "Mar")

udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "Feb")
udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "FebMar")
udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.3, 
               n.ci.thresh = 3, iso.subset = "off", drop.months = "Mar")
```

```{r Chunk 6, eval = TRUE}
source("code/4.7.summarising_udi_by_sp_size.R")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Feb")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "FebMar")
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; root.selection = "exp"; iso.subset = "off"
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Jan")

summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "FebMar")
summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Feb")
summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "on", drop.months = "Mar")

summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "Feb")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "FebMar")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "Mar")

summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "FebMar")
summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "Feb")
summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "exp", iso.subset = "off", drop.months = "Mar")
```

```{r Chunk 7, eval = TRUE}
source("code/10.Comparison_with_Meinzer1999.R")
iso.compare(goodness.fit = 0.3, dryseason = "on", 
            root.selection = "exp", iso.subset = "on", drop.months = "None")
iso.compare(goodness.fit = 0.3, dryseason = "on", 
            root.selection = "exp", iso.subset = "on", drop.months = "JanFebMar")
iso.compare(goodness.fit = 0.3, dryseason = "on", 
            root.selection = "exp", iso.subset = "on", drop.months = "JanFeb")
iso.compare(goodness.fit = 0.3, dryseason = "on", 
            root.selection = "exp", iso.subset = "on", drop.months = "Jan")
# goodness.fit = 0.3; dryseason = "on"; root.selection = "exp"; iso.subset = "on"; drop.months = "None"
```
